---
title: "MWI_emod_postprocess"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/gpfs/data/bershteynlab/EMOD/citrod01/MWI_calib_original_20220122')
```

# Postprocessing MWI model outputs

The collaborators working with us on Malawi want us to produce a standardized set of results. The purpose of this notebook will be to write out scripts which will produce the summary statistics that we need.

The secondary purpose of this notebook will be to produce example scripts which will be compatible with David Kaftan's EMODAnalyzeR library, and add capabilities to his analyzers.

```{r Load libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```

# Read in simulation stuff
```{r}
sim.results <- EMODAnalyzeR::read.simulation.results.bigpurple(
  #experiment_path = "/gpfs/scratch/citrod01/experiments/Malawi--0.01--rep3--test2_iter20___2022_04_09_05_03_57_150118",
  #experiment_path = "/gpfs/scratch/citrod01/experiments/Baseline-campaign_Malawi_1Dec2021_recalib-Baseline___2022_04_12_18_14_09_084274",
  experiment_path = "/gpfs/scratch/citrod01/experiments/Baseline-campaign_Malawi_1Dec2021_recalib-Baseline___2022_04_13_18_51_19_742598",
  scenario_name = 'baseline',
  summarize_columns = c("Newly.Infected", "Newly.Tested.Positive", "Newly.Tested.Negative",
                        "Population","Infected", "On_ART","Died", "Died_from_HIV",
                        "Tested.Past.Year.or.On_ART", "Tested.Ever","Diagnosed",
                        "HCTTestingLoop1","ARTStaging9","HCTTestingLoop0",
                        "Needs_PMTCT_Diagnostic_Test","HIV_Positive_at_ANC","HIV_Negative_at_ANC_NULL",
                        "ARTStaging0","ARTStaging1","ARTStaging_Negative_NULL"),
  stratify_columns = c("Year", "Gender", "Age","IP_Key.Risk","IsCircumcised"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
) %>% 
  ungroup()

```


# Population rescaling factor
Need to scale up everything, for rescaling extensible variables
```{r Population rescaling factor}
CENSUS_YEAR = 2018.5
MALAWI_CENSUS_POP = 17563749

sim.results.pop.scaling <- sim.results %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = MALAWI_CENSUS_POP/total.pop)

sim.results <- sim.results %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )
```


# Population
I am going to make the choice to use the half-year points to mark population
```{r Population}
# Males 15+ 
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, sim.id, pop.scaling.factor) %>%
  filter(Gender == 0, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  # remember to rescale by population scaling factor!
  summarize(Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.pop.males = mean(Population), .groups = 'keep')

# Females 15+
p2 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, sim.id, pop.scaling.factor) %>%
  filter(Gender == 1, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.pop.females = mean(Population), .groups = 'keep')

# Children <15
p3 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, sim.id, pop.scaling.factor) %>%
  filter(Age < 15, ceiling(Year) != Year) %>%
  group_by(Year, sim.id) %>% 
  summarize(Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.pop.children = mean(Population), .groups = 'keep')

# Overall
p4 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.pop.overall = mean(Population), .groups = 'keep')

pop.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

pop.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```


# PLHIV
This is like prevalence, but without the population denominator.
Again I am going to use the half-year points to count people living with HIV

```{r People living with HIV}
# Males 15+ 
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Infected, sim.id, pop.scaling.factor) %>%
  filter(Gender == 0, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.plhiv.males = mean(Infected), .groups = 'keep')

# Females 15+
p2 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Infected, sim.id, pop.scaling.factor) %>%
  filter(Gender == 1, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.plhiv.females = mean(Infected), .groups = 'keep')

# Children <15
p3 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Infected, sim.id, pop.scaling.factor) %>%
  filter(Age < 15, ceiling(Year) != Year) %>%
  group_by(Year, sim.id) %>% 
  summarize(Infected = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.plhiv.children = mean(Infected), .groups = 'keep')

# Overall
p4 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Infected, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.plhiv.overall = mean(Infected), .groups = 'keep')

plhiv.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year))

plhiv.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# Count number of new HIV infections
This is going to be on a per-year basis, so I will need to use a similar trick here to sum over each pair of observation points for each year. 
This is still an absolute count, so will need to scale up the number newly infected
```{r New Infections}
# Males 15-49
p1 <- sim.results %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, Newly.Infected) %>% 
  # rescale by population scale factor
  inner_join(sim.results.pop.scaling, by = c("sim.id")) %>%
  group_by(Year, Gender, sim.id) %>% 
  summarize(Newly.Infected = sum(Newly.Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.new.infections.males = mean(Newly.Infected), .groups = 'keep')

# Females 15-24
p2 <- sim.results %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, Newly.Infected) %>% 
  # rescale by population scale factor
  inner_join(sim.results.pop.scaling, by = c("sim.id")) %>%
  group_by(Year, Gender, sim.id) %>% 
  summarize(Newly.Infected = sum(Newly.Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.new.infections.females.younger = mean(Newly.Infected), .groups = 'keep')

# Females 25-49
p3 <- sim.results %>% 
  filter(Gender == 1, Age >=25, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, Newly.Infected) %>% 
  # rescale by population scale factor
  inner_join(sim.results.pop.scaling, by = c("sim.id")) %>%
  group_by(Year, Gender, sim.id) %>% 
  summarize(Newly.Infected = sum(Newly.Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.new.infections.females.older = mean(Newly.Infected), .groups = 'keep')

# Overall
p4 <- sim.results %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, Newly.Infected) %>% 
  # rescale by population scale factor
  inner_join(sim.results.pop.scaling, by = c("sim.id")) %>%
  group_by(Year, sim.id) %>% 
  summarize(Newly.Infected = sum(Newly.Infected*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.new.infections.overall = mean(Newly.Infected), .groups = 'keep')

new.inf.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

new.inf.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# HIV-caused deaths
Count the number of deaths from HIV
```{r HIV-caused deaths}
# Males 15+ 
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Died_from_HIV, sim.id, pop.scaling.factor) %>%
  filter(Gender == 0, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  # Rescale by population scaling factor
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.hivdeaths.males = mean(Died_from_HIV), .groups = 'keep')

# Females 15+
p2 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Died_from_HIV, sim.id, pop.scaling.factor) %>%
  filter(Gender == 1, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  # Rescale by population scaling factor
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.hivdeaths.females = mean(Died_from_HIV), .groups = 'keep')

# Children <15
p3 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Died_from_HIV, sim.id, pop.scaling.factor) %>%
  filter(Age < 15, ceiling(Year) != Year) %>%
  group_by(Year, sim.id) %>% 
  # Rescale by population scaling factor
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>%
  group_by(Year) %>% 
  summarize(mean.hivdeaths.children = mean(Died_from_HIV), .groups = 'keep')

# Overall
p4 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Died_from_HIV, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  # Rescale by population scaling factor
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>%
  group_by(Year) %>% 
  summarize(mean.hivdeaths.overall = mean(Died_from_HIV), .groups = 'keep')

hiv.deaths.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year))

hiv.deaths.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# All deaths
```{r All-cause deaths}
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Died, sim.id, pop.scaling.factor) %>%
  filter(Gender == 0, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Died = sum(Died*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.deaths.males = mean(Died), .groups = 'keep')

# Females 15+
p2 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Died, sim.id, pop.scaling.factor) %>%
  filter(Gender == 1, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Died = sum(Died*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.deaths.females = mean(Died), .groups = 'keep')

# Overall
p3 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Died, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Died = sum(Died*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(mean.deaths.overall = mean(Died), .groups = 'keep')

deaths.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  mutate(Year = floor(Year)) 

deaths.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# HIV Prevalence
This is calculated at each time step as number infected divided by the population

The MIHPSA report wants to find FSW and MSM prevalences, but I don't think I'm able to do that with the reports 
```{r Prevalence }
# Males 15-24 
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Gender == 0, Age >= 15, Age <25, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>% 
  group_by(Year) %>% 
  summarize(mean.prev.males.younger = mean(Prevalence), .groups = 'keep')
  
# Males 25-49
p2 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Gender == 0, Age >= 25, Age <50, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>% 
  group_by(Year) %>% 
  summarize(mean.prev.males.older = mean(Prevalence), .groups = 'keep')

# Females 15-24
p3 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Gender == 1, Age >= 15, Age <25, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>% 
  group_by(Year) %>% 
  summarize(mean.prev.females.younger = mean(Prevalence), .groups = 'keep')
  
# Females 25-49
p4 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Gender == 1, Age >= 25, Age <50, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>% 
  group_by(Year) %>% 
  summarize(mean.prev.females.older = mean(Prevalence), .groups = 'keep')

# Children <15
p5 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Age < 15, ceiling(Year) != Year) %>%
  group_by(Year, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>%
  group_by(Year) %>% 
  summarize(mean.prev.children = mean(Prevalence), .groups = 'keep')

# Female Sex Workers
p6 <- sim.results %>% 
  filter(Gender == 1, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(ceiling(Year) != Year) %>%
  group_by(Year, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>%
  group_by(Year) %>% 
  summarize(mean.prev.fsw = mean(Prevalence), .groups = 'keep')


# Overall
p7 <-sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>%
  group_by(Year) %>% 
  summarize(mean.prev.overall = mean(Prevalence), .groups = 'keep')


prev.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  mutate(Year = floor(Year)) 

prev.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# HIV Incidence
The MIHPSA report asks us to calculate the per-100-p-y incidence, but I am not clear on how to get this number out. Is the per-year calculation a per 1 person year? So maybe it's dividing this number by 100?

```{r Incidence}
# Males 15-24
p1 <- sim.results %>% 
  filter(Gender == 0, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(mean.inc.males.younger = mean(incidence), .groups = 'keep')

# Males 25-49
p2 <- sim.results %>% 
  filter(Gender == 0, Age >=25, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(mean.inc.males.older = mean(incidence), .groups = 'keep')

# Females 15-24
p3 <- sim.results %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(mean.inc.females.younger = mean(incidence), .groups = 'keep')

# Females 25-49
p4 <- sim.results %>% 
  filter(Gender == 1, Age >=25, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(mean.inc.females.older = mean(incidence), .groups = 'keep')

# Overall
p5 <- sim.results %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  # Still disaggregated by gender, so let's aggregate up
  group_by(Year, sim.id, scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), pop = sum(`Population - Infected`)) %>% 
  mutate(incidence = Newly.Infected/(pop - Newly.Infected/2)) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(mean.inc.overall = mean(incidence), .groups = 'keep')

inc.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>% 
  mutate(Year = floor(Year)) 

inc.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# PLHIV aware of their status
This is people who have been diagnosed - will need to double-check that the "Diagnosed" column from the simulation results reflects a running total of the people who know their HIV status:
```{r Diagnosed}
plhiv.diagnosed.summary <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Diagnosed, Infected, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Diagnosed = sum(Diagnosed*pop.scaling.factor), Infected = sum(Infected*pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(PLHIV.Diagnosed = case_when(Infected == 0 ~ 0,
                                     Infected > 0 ~ Diagnosed/Infected) ) %>%
  group_by(Year) %>% 
  summarize(mean.plhiv.diagnosed = mean(PLHIV.Diagnosed), .groups = 'keep') %>% 
  mutate(Year = floor(Year)) 

plhiv.diagnosed.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# Total tests and fraction of positive tests
Total tests performed = Newly.Tested.Positive + Newly.Tested.Negative
Just as for incidence, I am going to have to combine everything by year. I'll create a function for doing this similar to the one that David made for incidence calculation.

```{r Total Tests Performed Over Age 15}
total.tests.summary <- sim.results %>% 
  filter(Age >= 15) %>% 
  EMODAnalyzeR::calculate.tests.performed(gender.breakdown = TRUE) %>% 
  inner_join(sim.results.pop.scaling, by = c("sim.id")) %>% 
  group_by(Year, Gender) %>% 
  summarize(mean.Total.Tests = mean(Total.Tests*pop.scaling.factor), .groups = 'keep') %>% 
  mutate(Gender_labels = case_when(Gender == 0 ~ "mean.Total.Tests.males", 
                                   Gender == 1 ~ "mean.Total.Tests.females")) %>% 
  pivot_wider(id_cols = Year, 
              names_from = Gender_labels,
              values_from = mean.Total.Tests) %>% 
  mutate(mean.Total.Tests = mean.Total.Tests.males + mean.Total.Tests.females)

total.tests.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value) %>% head
```

```{r Fraction of positive tests for adults}

positive.tests.summary <- sim.results %>% 
  filter(Age > 15) %>% 
  EMODAnalyzeR::calculate.tests.performed(gender.breakdown = FALSE) %>% 
  group_by(Year) %>% 
  summarize(mean.Proportion.Positive.Tests = mean(Proportion.Positive.Tests))

positive.tests.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# PLHIV on ART
Count the number of people on art. Art coverage is the ratio between people on art and PLHIV.

```{r OnART}
# Males Age 15+
p1 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, On_ART, Infected, sim.id, pop.scaling.factor) %>%
  filter(Gender == 0, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(On_ART = sum(On_ART*pop.scaling.factor), Infected = sum(Infected*pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(ART.coverage = case_when(Infected == 0 ~ 0,
                                  Infected > 0 ~ On_ART/Infected)) %>% 
  group_by(Year) %>% 
  summarize(mean.On_ART.males = mean(On_ART), mean.ART.coverage.males = mean(ART.coverage), .groups = 'keep')

# Females Age 15+
p2 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, On_ART, Infected, sim.id, pop.scaling.factor) %>%
  filter(Gender == 1, Age >= 15, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(On_ART = sum(On_ART*pop.scaling.factor), Infected = sum(Infected*pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(ART.coverage = case_when(Infected == 0 ~ 0,
                                  Infected > 0 ~ On_ART/Infected)) %>% 
  group_by(Year) %>% 
  summarize(mean.On_ART.females = mean(On_ART), mean.ART.coverage.females = mean(ART.coverage), .groups = 'keep')

# Children
p3 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, On_ART, Infected, sim.id, pop.scaling.factor) %>%
  filter(Age < 15, ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(On_ART = sum(On_ART*pop.scaling.factor), Infected = sum(Infected*pop.scaling.factor), 
            .groups = 'keep') %>%   
  mutate(ART.coverage = case_when(Infected == 0 ~ 0,
                                  Infected > 0 ~ On_ART/Infected)) %>% 
  group_by(Year) %>% 
  summarize(mean.On_ART.children = mean(On_ART), mean.ART.coverage.children = mean(ART.coverage), .groups = 'keep')

# Total
p4 <- sim.results %>% 
  dplyr::select(Year, Gender, Age, On_ART, Infected, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id) %>% 
  summarize(On_ART = sum(On_ART*pop.scaling.factor), Infected = sum(Infected*pop.scaling.factor), 
            .groups = 'keep') %>% 
  mutate(ART.coverage = case_when(Infected == 0 ~ 0,
                                  Infected > 0 ~ On_ART/Infected)) %>% 
  group_by(Year) %>% 
  summarize(mean.On_ART.overall = mean(On_ART), mean.ART.coverage.overall = mean(ART.coverage), .groups = 'keep')


onart.data <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>% 
  mutate(Year = floor(Year)) 

onart.summary <- onart.data %>% select(Year, mean.On_ART.males, mean.On_ART.females, mean.On_ART.children, mean.On_ART.overall)

onart.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

```{r Art Coverage}
art.coverage.summary <- onart.data %>% 
  select(Year, mean.ART.coverage.males, mean.ART.coverage.females, 
         mean.ART.coverage.children, mean.ART.coverage.overall)

art.coverage.summary %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```


# VMMC

Fraction of males aged 15-49 who have been circumcised

Given that the data only seem to count people after 2015, which is when the VMMC program started in Malawi, 
```{r Circumcision fraction}
circumcision.summary <- sim.results %>% 
  dplyr::select(Year, Gender, Age, IsCircumcised, Population, sim.id) %>%
  filter(Gender == 0, Age >= 15, Age < 50, ceiling(Year) != Year) %>% 
  group_by(Year, Gender, sim.id, IsCircumcised) %>% 
  summarize(Population = sum(Population), .groups = 'keep') %>% 
  mutate(IsCircumcised.status = case_when(IsCircumcised == 0 ~ 'No', IsCircumcised == 1 ~ 'Yes')) %>% 
  pivot_wider(id_cols = c(Year, sim.id), names_from = IsCircumcised.status, values_from = Population) %>% 
  mutate(fraction.circumcised = Yes/(No + Yes)) %>% 
  group_by(Year) %>% 
  summarize(mean.fraction.circumcised = mean(fraction.circumcised), .groups = 'keep') %>% 
  mutate(Year = floor(Year)) 

circumcision.summary  %>% 
  pivot_longer(-Year) %>% 
  pivot_wider(names_from = Year, values_from = value)
```

# Save everything as a csv:
```{r Output as csv}
rbind(pop.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # population
      plhiv.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # plhiv
      new.inf.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # new hiv infections
      hiv.deaths.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # hiv deaths
      deaths.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # total deaths
      prev.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # prevalence
      inc.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # incidence
      plhiv.diagnosed.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # plhiv aware of their status
      total.tests.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # total tests performed
      positive.tests.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # positive tests performed
      onart.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # number of plhiv on art
      art.coverage.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value), # art coverage summary
      circumcision.summary %>% pivot_longer(-Year) %>% pivot_wider(names_from = Year, values_from = value) # circumcisions
) %>% 
  write.csv(file = '/gpfs/data/bershteynlab/EMOD/citrod01/MWI_calib_original_20220122/MWI_MIHPSA/MIHPSA_results_report.csv')
```


# Plots for comparison with data

## Read Prevalence 
```{r Read Prevalence data}
# Read in the calibration targets data
prev.target <- read_csv("calib_targets_data/MalawiNationalPrevalence.csv")

# Convenient relabels of age bins
prev.target$Age = factor(prev.target$AgeBin, 
                         levels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)", "[15:50)"),
                         labels = c(1:11)
                         )

prev.target$Year.label = factor(prev.target$Year, 
                          levels = c(2004.0, 2010.0, 2015.0, 2015.5),
                          labels = c( "2004 (DHS)","2010 (DHS)", "2015 (DHS)", "2015 (PHIA)"))
```

```{r Read Incidence data}
# Using the new Incidence data, which has the right age bins for fair comparison to the reports
inc.target <- read_csv("calib_targets_data/Malawi_Incidence_new.csv")

inc.target$Year = factor(inc.target$Year, levels = c("2015.5"), labels = c("2015 (PHIA)"))

inc.target$Age = factor(inc.target$AgeBin, 
                        levels = c("[15:50)", "[15:25)", "[25:35)", "[35:50)"),
                        labels = c(1,2,3,4))


# This is the missing row from the incidence data
```

```{r Read ART coverage data}
onart.target <- read_csv("calib_targets_data/Malawi_OnART.csv")

#art.cov.target <- read_csv("calib_targets_data/ARTCoverage.csv")
#art.cov.target <- art.cov.target %>% filter(Province=='All')
# art.cov.target$Year.label = factor(art.cov.target$Year, 
#                           levels = c(2004.0, 2010.0, 2015.0, 2015.5),
#                           labels = c( "2004 (DHS)","2010 (DHS)", "2015 (DHS)", "2015 (PHIA)"))

art.cov.target <- read_csv("calib_targets_data/ART_Coverage_PHIA.csv")
art.cov.target$Year = 2015.5
art.cov.target$Year.label = factor(art.cov.target$Year, 
                                   levels = c(2015.5), labels = c("2015 (PHIA)"))

# Convenient relabels of age bins
art.cov.target$Age = factor(art.cov.target$AgeBin, 
                         levels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)", "[15:50)"),
                         labels = c(1:11)
                         )
# Relabel and subset useful columns
art.cov.target <- art.cov.target %>% 
  dplyr::select("Year", "Year.label", "Age", "AgeBin", "Gender" = "gender", "ARTCoverage", "denominator", "confidence_lower", "confidence_upper")
```

## Prevalence plots
Plot all ages prevalence over time
```{r All ages prevalence plot}
prev.data <- sim.results %>% 
  dplyr::select(Year, Gender, Age, Population, Infected, sim.id) %>%
  filter(Age >= 15, Age < 49) %>% 
  group_by(Year, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population), .groups = 'keep') %>% 
  mutate(Prevalence = Infected/Population) %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female")) 

prev.plot <- ggplot() +
  # plot ensemble of runs
  geom_point(data = prev.data, mapping = aes(x = Year, y = Prevalence), size = .25, alpha = .1, color = 'gray') + 
  # plot mean
  geom_point(data = prev.data %>% 
               group_by(Year, Gender) %>% 
               summarize(prevalence = mean(Prevalence), .groups = 'keep') , 
             mapping = aes(x = Year, y = prevalence), size = 1, color = 'blue') + 
  # compare to calibration targets
  geom_point(data = prev.target %>% filter(Age == 11), 
             size=2, color = "black", aes(x=Year, y=NationalPrevalence)) + 
  geom_errorbar(data = prev.target %>% filter(Age == 11), 
                aes(x=Year, ymin=lower, ymax=upper), color="black", width=2, size=1) +
  xlab("Year") +
  ylab("Prevalence, ages 15-49") +
  facet_grid(cols = vars(Gender)) + 
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,.2,0.05), limits=c(0,.20)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  scale_color_manual(values = c("red", "green", "blue"), breaks = c(1,2,3), labels = c("0.005", "0.01","0.05"), name = "Seed Coverage") + 
  theme(legend.position="top") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  
prev.plot
```

Plot age prevalence curves
```{r Plot age prevalence curves}
prev.data.age <- sim.results %>% 
  filter(Age >=15, Age <65, Year < 2050) %>% 
  group_by(Year, Age, Gender, sim.id) %>% 
  summarize(population = sum(Population), infected = sum(Infected), .groups = 'keep') %>% 
  mutate(prevalence = infected / population) %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female"))

# Need to apply the right labels to the age groups...
prev.data.age$AgeBin <- factor(prev.data.age$Age, 
                     levels = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60),
                     labels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)")
                     )
prev.data.age$AgeBin.index = prev.data.age$Age/5-2

ap.plot <- ggplot() + 
  geom_point(data = prev.target %>% filter(Age != 11) %>% ungroup(),
           mapping = aes(x = Age, y = NationalPrevalence), color = 'black') +
  geom_errorbar(data = prev.target %>% filter(Age != 11) %>% ungroup(),
                mapping = aes(x=Age, ymin=lower, ymax=upper), color="black", width=.3, size=1) +
  geom_point(
   data = prev.data.age %>% 
    ungroup() %>% 
    group_by(Age, AgeBin, AgeBin.index, Gender, Year) %>% 
    filter(Year %in% c(2015.5, 2010.0, 2004.0, 2015.0)) %>% 
    summarize(mean.prev = mean(prevalence), med.prev = median(prevalence),.groups = 'keep'),
    mapping = aes(x = AgeBin.index, y = mean.prev), color = 'blue') +
  facet_grid(cols = vars(Gender), rows = vars(Year)) + 
  scale_x_discrete(breaks = 1:10, 
                   labels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", 
                              "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)")
                     ) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,.35,0.05), limits=c(0,.3)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ap.plot
```


## Incidence Plots
```{r All ages incidence plots}
inc.table <- sim.results %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence(gender.breakdown = TRUE) %>% 
  # Still disaggregated by gender, so let's aggregate up
  group_by(Year, Gender, sim.id, scenario_name) %>% 
  summarize(Newly.Infected = sum(Newly.Infected), pop = sum(`Population - Infected`)) %>% 
  mutate(incidence = Newly.Infected/(pop - Newly.Infected/2)) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female"))

inc.plot <- ggplot() + 
  # plot the simulation results
  geom_point(data = inc.table, mapping = aes(x = Year, y = incidence), color = 'gray', alpha = .1) +
  geom_line(data = inc.table %>% 
                    group_by(Year, Gender) %>% 
                    summarize(mean.inc.overall = mean(incidence), .groups = 'keep'), 
            mapping = aes(x = Year, y = mean.inc.overall), size = 1, color = "blue") +
  # plot the calibration targets
  geom_point(data = inc.target %>% filter(Age == 1), 
             aes(x=2015, y=Incidence),
             size=2, color = "black") + 
  geom_errorbar(data = inc.target %>% filter(Age == 1), 
                aes(x=2015, ymin=lb, ymax=ub), 
                color="black", width=2, size=1) +
  facet_grid(cols = vars(Gender)) +
  xlab("Year") +
  ylab("Incidence, ages 15-49") +
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = .1), breaks = seq(0,.03,0.005), limits=c(0,.03)) +
  scale_x_continuous(breaks = seq(1980,2040,10)) +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  
inc.plot
```

Incidence by age plots
```{r Plot incidence by age}
# Need to bin ages to match the PHIA data
t1 <- sim.results %>% 
  filter(Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence(gender.breakdown = TRUE) %>% 
  # Still disaggregated by gender, so let's aggregate up
  group_by(Year, Gender, sim.id) %>%
  summarize(Newly.Infected = sum(Newly.Infected), pop = sum(`Population - Infected`)) %>% 
  mutate(incidence = Newly.Infected/(pop - Newly.Infected/2)) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year, Gender) %>% 
  summarize(mean.inc.overall = mean(incidence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female")) %>% 
  mutate(Age = 2)

t2 <- sim.results %>% 
  filter(Age >=25, Age < 35) %>% 
  EMODAnalyzeR::calculate.incidence(gender.breakdown = TRUE) %>% 
  # Still disaggregated by gender, so let's aggregate up
  group_by(Year, Gender, sim.id) %>%
  summarize(Newly.Infected = sum(Newly.Infected), pop = sum(`Population - Infected`)) %>% 
  mutate(incidence = Newly.Infected/(pop - Newly.Infected/2)) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year, Gender) %>% 
  summarize(mean.inc.overall = mean(incidence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female")) %>% 
  mutate(Age = 3)

t3 <- sim.results %>% 
  filter(Age >=35, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence(gender.breakdown = TRUE) %>% 
  # Still disaggregated by gender, so let's aggregate up
  group_by(Year, Gender, sim.id) %>%
  summarize(Newly.Infected = sum(Newly.Infected), pop = sum(`Population - Infected`)) %>% 
  mutate(incidence = Newly.Infected/(pop - Newly.Infected/2)) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year, Gender) %>% 
  summarize(mean.inc.overall = mean(incidence), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female")) %>% 
  mutate(Age = 4)


inc.age.data <- t1 %>% pivot_wider(id_cols = c("Year", "Gender"), 
                                   names_from = c("Age"), 
                                   values_from = c("mean.inc.overall")) %>% 
  inner_join(t2 %>% pivot_wider(id_cols = c("Year", "Gender"), 
                                names_from = c("Age"), 
                                values_from = c("mean.inc.overall")), 
             by = c("Year", "Gender")) %>% 
  inner_join(t3 %>% pivot_wider(id_cols = c("Year", "Gender"), 
                              names_from = c("Age"), 
                              values_from = c("mean.inc.overall")), 
           by = c("Year", "Gender")) %>% 
  pivot_longer(cols = c( `2`, `3`,`4`), names_to = c("AgeBin"), values_to = c("mean.inc"))

inc.age.plot <- ggplot() + 
  geom_point(data = inc.target %>% filter(Age != 1), 
             mapping = aes(x = Age, y = Incidence)) + 
  geom_errorbar(data = inc.target %>% filter(Age != 1), 
                mapping = aes(x=Age, ymin=lb, ymax=ub), color="black", width=.3, size=1) +
  geom_point(data = inc.age.data %>% filter(Year == 2015) %>% mutate(Year = "2015 (PHIA)"),
             mapping = aes(x = AgeBin, y = mean.inc), color = "blue"
             ) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) + 
  scale_x_discrete(breaks = 2:4, 
                   labels = c("[15:25)", "[25:35)", "[35:50)")
                   ) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = .1), 
                     breaks = seq(0,.0125,0.005), 
                     limits=c(0,.0125)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

inc.age.plot
```


## ART Plots

```{r Number of people on ART}
onart.data <- sim.results %>% 
  dplyr::select(Year, Gender, Age, On_ART, Infected, sim.id, pop.scaling.factor) %>%
  filter(ceiling(Year) != Year) %>% 
  group_by(Year, sim.id, Gender) %>% 
  summarize(On_ART = sum(On_ART*pop.scaling.factor), .groups = 'keep') %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female"))
  
onart.plot <- ggplot() + 
  geom_point(data = onart.data, mapping = aes(x = Year, y = On_ART),
             size = 1, alpha = .1, color = 'gray') +
  geom_line(data = onart.data %>%
              group_by(Year, Gender) %>%
              summarize(mean.On_ART.overall = mean(On_ART), 
                        .groups = 'keep'),
            color = 'blue', size = 1,
            mapping = aes(x = Year, y = mean.On_ART.overall)) + 
  geom_point(data = onart.target, 
             mapping = aes(x = Year, y = On_ART)) + 
  geom_errorbar(data = onart.target, 
                mapping = aes(x = Year, ymin = lower, ymax = upper)) + 
  facet_grid(cols = vars(Gender))  + 
  ylab("Numer on ART, Ages 15+")+
  theme_bw(base_size=16) +
  guides(fill = guide_legend(keywidth = 2, keyheight = 1)) +
  scale_y_continuous(limits=c(0,750000), breaks = seq(0,750000,250000), expand=c(0,0)) +
  scale_x_continuous(limits = c(2000,2025), breaks = seq(2000,2025,5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(strip.background = element_rect(colour="black", fill="white")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

onart.plot
```


ART coverage by age
I am not sure whether the denominator here is supposed to be PLHIV or total population.  I am not able to 
```{r ART coverage by age}

oac.data.age <- sim.results %>% 
  filter(Age >=15, Age < 65, Year == 2015.5) %>% 
  group_by(Year, Age, Gender, sim.id) %>% 
  summarize(oac.pop = sum(On_ART), population = sum(Infected), .groups = 'keep') %>% 
  mutate(onart.coverage = case_when(population <= 0 ~ 0,
                                population > 0 ~ oac.pop/population)) %>% 
  mutate(Gender = case_when(Gender == 0 ~ "Male", Gender == 1 ~ "Female")) %>% 
  group_by(Year, Age, Gender) %>% 
  summarize(mean.onart.coverage = mean(onart.coverage), .groups = 'keep')

# Need to apply the right labels to the age groups...
oac.data.age$AgeBin <- factor(oac.data.age$Age, 
                     levels = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60),
                     labels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)")
                     )
oac.data.age$AgeBin.index = oac.data.age$Age/5-2

oac.plot <- ggplot() + 
  geom_point(data = art.cov.target %>% filter(Age != 11) %>% ungroup(),
           mapping = aes(x = Age, y = ARTCoverage/100), color = 'black') +
  geom_errorbar(data = art.cov.target %>% filter(Age != 11) %>% ungroup(),
                mapping = aes(x=Age, ymin=confidence_lower/100, ymax=confidence_upper/100), color="black", width=.3, size=1) +
  geom_point(
    data = oac.data.age %>%
    ungroup() %>%
    group_by(Age, AgeBin, AgeBin.index, Gender, Year) %>%
    filter(Year %in% c(2015.5, 2010.0, 2004.0, 2015.0)),
    mapping = aes(x = AgeBin.index, y = mean.onart.coverage), color = 'blue') +
  facet_grid(cols = vars(Gender), rows = vars(Year)) + 
  scale_x_discrete(breaks = 1:10, 
                   labels = c("[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", 
                              "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)")
                     ) + 
  #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0,.35,0.05), limits=c(0,.3)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

oac.plot

```

